---
title: "tutorial 5 _A0100125H"
author: "jy"
date: "February 25, 2016"
output: md_document
---

```{r, message=FALSE, echo=FALSE}
library(Rcmdr)
library(car)
library(RcmdrMisc)
library(foreign, pos=15)
country <- read.spss("C:/Users/ASUS/Documents/country122.sav", 
  use.value.labels=TRUE, max.value.labels=Inf, to.data.frame=TRUE)
colnames(country) <- tolower(colnames(country))
RegModel <- lm(lifeexpf~birthrat, data=country)
summary(RegModel)
```

* As p-value: < 2.2e-16 (less than 0.05) is small, we cannot reject null hypothesis. Thus, there is a linear relationship between the two variables.

* R-square is 0.756 close to 1, showing a relatively strong linear relationship between the two variables.

```{r, echo=FALSE}
scatterplot(lifeexpf~birthrat, reg.line=lm, smooth=FALSE, spread=FALSE, 
  boxplots=FALSE, span=0.5, ellipse=FALSE, levels=c(.5, .9), jitter=list(x=1),
   data=country)
```

* The two variables are negatively corelated (as seen from the graph - downward slope). The higher the birth rate, the lower the life expectancy.

* Simple linear equation: lifeexpf = 89.58892 - 0.74471 * birthrat;
  lifeexpf = 89.58892 - 0.74471 * 25 = 70.97117
