---
title: "IS4250 Group18 Project Code"
author: "jy"
date: "April 5, 2016"
output: md_document
---

##### Import library

```{r,  message=FALSE, echo=FALSE}
library(MASS)
library(effects)
library(vcd)
library(car)
library(mlogit)
library(nnet)
library(dplyr)
library(data.table)
library(ggplot2)
library(lattice)
```

##### Convert excel data file into .csv format. Read all data from csv file in R.

```{r,  message=FALSE, echo=FALSE}
OriginalHealthData <- read.csv("C:/Users/ASUS/Documents/Health Data.csv")
healthData <- dplyr::select(OriginalHealthData, everything())
```

##### Rename 24 data attributes according to codebook provided. 
##### (Detected some discrepency and several missing attributes such as self-reported health status)

```{r,  message=FALSE, echo=FALSE}
healthData <- dplyr::rename(healthData, Occupation = b1)
healthData <- dplyr::rename(healthData, WorkplaceScale = b2)
healthData <- dplyr::rename(healthData, Gender = q102)
healthData <- dplyr::rename(healthData, Age = q103)
healthData <- dplyr::rename(healthData, MaritalStatus = q104)
healthData <- dplyr::rename(healthData, EducationAttainment = q105)
healthData <- dplyr::rename(healthData, AccompanyChild = q106)
healthData <- dplyr::rename(healthData, Salary = q107)
healthData <- dplyr::rename(healthData, YearsAsMigrant = q108a1)
healthData <- dplyr::rename(healthData, NumberOfCitiesResidedIn = q108a2)
healthData <- dplyr::rename(healthData, DailyWorkingHours = q108b)
healthData <- dplyr::rename(healthData, WeeklyWorkingDays = q108c1)
healthData <- dplyr::rename(healthData, TypeOfResidence = q108c2)
healthData <- dplyr::rename(healthData, HundredCigarettes = q410)
healthData <- dplyr::rename(healthData, CurrentSmoker = q411)
healthData <- dplyr::rename(healthData, NumberOfCigarettesPerDay = q412)
healthData <- dplyr::rename(healthData, DrinkingFrequency = q431)
healthData <- dplyr::rename(healthData, AlcoholDrinksPerDay = q432)
healthData <- dplyr::rename(healthData, SixOrMoreDrinksFrequency = q433)
healthData <- dplyr::rename(healthData, DailySleepingHours = q444)
healthData <- dplyr::rename(healthData, SleepingQuality = q446)
healthData <- dplyr::rename(healthData, DailyBreakfast = q450)
healthData <- dplyr::rename(healthData, DailyFruitsVegetables = q451)
healthData <- dplyr::rename(healthData, DailyRegularMeals = q452)
```

##### Compute Mental Health Score:
* Read self-assessment scores of q201-q290, 90 questions from Symptom Checklist-90-Revised. 
* Each question carries 1-5 marks, representing none, mild, moderate, severe, extreme.
* Sum up 90 scores

```{r,  message=FALSE, echo=FALSE}
mentalChecklist <- dplyr::select(OriginalHealthData, contains("q2"))
mentalChecklist <- mentalChecklist %>% transmute(MentalHealth = q201 + q202 + q203 + q204 +q205 + q206 + q207 + q208 +q209 + q210 + q211 + q212 + q213 + q214 + q215 + q216 + q217 + q218 + q219 + q220 + q221 + q222 + q223 + q224 + q225 + q226 + q227 + q228 + q229 + q230 + q231 + q232 + q233 + q234 + q235 + q236 + q237 + q238 + q239 + q240 + q241 + q242 + q243 + q244 + q245 + q246 + q247 + q248 + q249 + q250 + q251 + q252 + q253 + q254 + q255 + q256 + q257 + q258 + q259 + q260 + q261 + q262 + q263 + q264 + q265 + q266 + q267 + q268 + q269 + q270 + q271 + q272 + q273 + q274 + q275 + q276 + q277 + q278 + q279 + q280 + q281 + q282 + q283 + q284 + q285 + q286 + q287 + q288 + q289 + q290)
healthData <- dplyr::bind_cols(healthData, mentalChecklist)
```

##### Compute Drinking Behaviour Score
* 3 question 
  + Frequency of drinking 
  + How many drinks containing alcohol do you have on a typical day when you are drinking?
  + How often do you have six or more drinks on one occasion?
* Each question carries 1-5 marks, representing degree of alcohol consumption
* Sum up 3 scores

```{r,  message=FALSE, echo=FALSE}
drinkingStatus <- dplyr::select(healthData, DrinkingFrequency, AlcoholDrinksPerDay, SixOrMoreDrinksFrequency)
drinkingStatus <- drinkingStatus %>% transmute(AlcoholConsumption = DrinkingFrequency + AlcoholDrinksPerDay + SixOrMoreDrinksFrequency - 3)
healthData <- dplyr::bind_cols(healthData, drinkingStatus)
```

##### Further process data (mainly Categorization)
* Education Attainment
  + 4 catrgories: Elementary or lower, Junior high school, High school, College or above
* Gender
  + swap sequence into 2 categories: Male, Female
* Number of Accompanying Children
  + 3 categories: No children, Cohabitating children, Children residing elsewhere
* Salary
  + 4 categories: <1500RMB, 1500-2500RMB, 2500-3500RMB, >=3500RMB
* Number of Cities Resided in
  + 2 categories: 1-2, >=3
* Daily Working Hours
* Weekly Working Days
* BMI:
  + BMI = weight(kg) / (height(m)^2)
  + 3 categories: < 18.5; >= 18.5 and < 24; >=24
* Mental Health
  + 2 categories: if MentalHealth score <= 160, Normal; if MentalHealth score > 160, Abnormal
* Smoking 
  + Current Smoker
  + 2 categories: Unhealthy, Healthy
  + if smoked in the past 30 days, Unhealthy; else Healthy
* Drinking 
  + Hazardous Alcohol Consumption
  + 2 categories: Unhealthy, Healthy
  + if Alcohol Consumption Score >=4 for Male or Alcohol Consumption Score >=3 for Female, Unhealthy; else Healthy
* Daily Sleeping Hours
  + 2 categories: Unhealthy, Healthy
  + if Daily Sleeping Hours 7-9 hours/night, Health; else Unhealthy
* Sleeping Quality
  + 2 categories: 1-2 Good/Fair; 3-4 Poor/Very Poor
* Daily Breakfasts
  + 2 categories: Unhealthy, Healthy
  + if almost Daily Breakfasts, Health; else Unhealthy
* Daily Fruits and Vegetables Consumption
  + 2 categories: Unhealthy, Healthy
  + if almost Daily Fruits and Vegetables Consumption, Health; else Unhealthy
* Daily Regular Meals
  + 2 categories: Unhealthy, Healthy
  + if almost Daily Regular Meals, Health; else Unhealthy

```{r,  message=FALSE, echo=FALSE}
healthData <- dplyr::mutate(healthData, EducationAttainmentX = ifelse(EducationAttainment == 1, 1, ifelse(EducationAttainment == 2, 2, ifelse(EducationAttainment == 3, 3, 4))))
healthData <- dplyr::mutate(healthData, BMI = weight/(height/100)/(height/100))
healthData <- dplyr::mutate(healthData, BMIX = ifelse(BMI < 18.5, 1, ifelse(BMI < 24, 2, 3)))
healthData <- dplyr::mutate(healthData, GenderX = ifelse(Gender == 1, 2, 1))
healthData <- dplyr::mutate(healthData, AgeX = ifelse(Age <= 32, 1, 2))
healthData <- dplyr::mutate(healthData, AccompanyChildX = ifelse(AccompanyChild == 1, 1, ifelse(AccompanyChild == 4, 3, 2)))
healthData <- dplyr::mutate(healthData, SalaryX = ifelse(Salary == 1, 1, ifelse(Salary == 2, 2, ifelse(Salary == 3, 3, 4))))
healthData <- dplyr::mutate(healthData, NumberOfCitiesResidedInX = ifelse(NumberOfCitiesResidedIn <= 2, 1, 2))
healthData <- dplyr::mutate(healthData, DailyWorkingHoursX = ifelse(DailyWorkingHours == 8, 1, ifelse(DailyWorkingHours < 8, 2, ifelse(DailyWorkingHours < 11, 3, 4))))
healthData <- dplyr::mutate(healthData, WeeklyWorkingDaysX = ifelse(WeeklyWorkingDays <= 4, 1, ifelse(WeeklyWorkingDays == 5, 2, ifelse(WeeklyWorkingDays == 6, 3, 4))))
healthData <- dplyr::mutate(healthData, MentalHealthX = ifelse(MentalHealth <= 160, 1, 2))
healthData <- dplyr::mutate(healthData, CurrentSmokerX = ifelse(CurrentSmoker == 1 | is.na(CurrentSmoker), 0, 1))
healthData <- dplyr::mutate(healthData, HazardousDrinkX = ifelse(AlcoholConsumption >= 4, 1, ifelse(GenderX == 2 & AlcoholConsumption == 3, 1, 0)))
healthData <- dplyr::mutate(healthData, DailySleepingHoursX = ifelse(DailySleepingHours < 7 | DailySleepingHours > 9, 1, 0))
healthData <- dplyr::mutate(healthData, SleepingQualityX = ifelse(SleepingQuality <= 2, 0, 1))
healthData <- dplyr::mutate(healthData, DailyBreakfastX = ifelse(DailyBreakfast == 1, 0, 1))
healthData <- dplyr::mutate(healthData, DailyFruitsVegetablesX = ifelse(DailyFruitsVegetables == 1, 0, 1))
healthData <- dplyr::mutate(healthData, DailyRegularMealsX = ifelse(DailyRegularMeals == 1, 0, 1))
```

##### Compute Lifestyle Behaviour Score
* 6 factors: CurrentSmoker, HazardousDrink, DailySleepingHours, DailyBreakfast, DailyFruitsVegetables, DailyRegularMeals
* 1 score for every Unhealthy Behavior
* Sum: 0, Healthy; 1-2 Relatively Healthy; 3-6 Unhealthy

```{r,  message=FALSE, echo=FALSE}
lifestyleScore <- dplyr::select(healthData, CurrentSmokerX, HazardousDrinkX, DailySleepingHoursX, DailyBreakfastX, DailyFruitsVegetablesX, DailyRegularMealsX)
lifestyleScore <- lifestyleScore %>% transmute(Score = CurrentSmokerX + HazardousDrinkX + DailySleepingHoursX + DailyBreakfastX + DailyFruitsVegetablesX + DailyRegularMealsX)
healthData <- dplyr::bind_cols(healthData, lifestyleScore)

healthData <- dplyr::mutate(healthData, ScoreX = ifelse(Score == 0, 1, ifelse(Score == 1 | Score == 2, 2, 3)))

healthDataTbl <- data.table(healthData)

```

##### Till here, end of Section 0 - Data Preparation


##### Section 1 - Chi-square Test for Socio-demographic characteristics of Rural-to-Urban Migrants by Gender

```{r,  message=FALSE, echo=FALSE}
Age <- table(healthDataTbl$AgeX, healthDataTbl$GenderX)
dimnames(Age) <- list(AgeX = c("<=32",">32"), GenderX = c("Male","Female"))

Age

chisq.test(Age,correct=F)

```
```{r,  message=FALSE, echo=FALSE}
Occupation <- table(healthDataTbl$Occupation, healthDataTbl$GenderX)
dimnames(Occupation) <- list(Occupation = c("Manufacturing","Construction","Hospitality","Domestic service", "Small business","Recreation/leisure"), GenderX = c("Male","Female"))

Occupation

chisq.test(Occupation,correct=F)

```

```{r,  message=FALSE, echo=FALSE}
WorkplaceScale <- table(healthDataTbl$WorkplaceScale, healthDataTbl$GenderX)
dimnames(WorkplaceScale) <- list(WorkplaceScale = c("Large","Moderate","Small"), GenderX = c("Male","Female"))

WorkplaceScale

chisq.test(WorkplaceScale,correct=F)

```

```{r,  message=FALSE, echo=FALSE}
EducationAttainment <- table(healthDataTbl$EducationAttainmentX, healthDataTbl$GenderX)
dimnames(EducationAttainment) <- list(EducationAttainmentX = c("Elementary or lower","Junior high school","High school","College"), GenderX = c("Male","Female"))

EducationAttainment

chisq.test(EducationAttainment,correct=F)

```

```{r,  message=FALSE, echo=FALSE}
MaritalStatus <- table(healthDataTbl$MaritalStatus, healthDataTbl$GenderX)
dimnames(MaritalStatus) <- list(MaritalStatus = c("Married","Single","Cohabitating","Divorced or widowed"), GenderX = c("Male","Female"))

MaritalStatus

chisq.test(MaritalStatus,correct=F)

```

```{r,  message=FALSE, echo=FALSE}
AccompanyChild <- table(healthDataTbl$AccompanyChildX, healthDataTbl$GenderX)
dimnames(AccompanyChild) <- list(AccompanyChildX = c("No children","Cohabitating children","Children residing elsewhere"), GenderX = c("Male","Female"))

AccompanyChild

chisq.test(AccompanyChild,correct=F)

```
```{r,  message=FALSE, echo=FALSE}
Salary <- table(healthDataTbl$SalaryX, healthDataTbl$GenderX)
dimnames(Salary) <- list(SalaryX = c("<1500RMB","1500-2500RMB","2500-3500RMB",">=3500RMB"), GenderX = c("Male","Female"))

Salary

chisq.test(Salary,correct=F)

```
```{r,  message=FALSE, echo=FALSE}
NumberOfCitiesResidedIn <- table(healthDataTbl$NumberOfCitiesResidedInX, healthDataTbl$GenderX)
dimnames(NumberOfCitiesResidedIn) <- list(NumberOfCitiesResidedInX = c("1-2", ">=3"), GenderX = c("Male","Female"))

NumberOfCitiesResidedIn

chisq.test(NumberOfCitiesResidedIn,correct=F)

```
```{r,  message=FALSE, echo=FALSE}
DailyWorkingHours <- table(healthDataTbl$DailyWorkingHoursX, healthDataTbl$GenderX)
dimnames(DailyWorkingHours) <- list(DailyWorkingHoursX = c("=8","<8","8-11",">=11"), GenderX = c("Male","Female"))

DailyWorkingHours

chisq.test(DailyWorkingHours,correct=F)

```
```{r,  message=FALSE, echo=FALSE}
WeeklyWorkingDays <- table(healthDataTbl$WeeklyWorkingDaysX, healthDataTbl$GenderX)
dimnames(WeeklyWorkingDays) <- list(WeeklyWorkingDaysX = c("<=4","5","6","7"), GenderX = c("Male","Female"))

WeeklyWorkingDays

chisq.test(WeeklyWorkingDays,correct=F)

```
```{r,  message=FALSE, echo=FALSE}
TypeOfResidence <- table(healthDataTbl$TypeOfResidence, healthDataTbl$GenderX)
dimnames(TypeOfResidence) <- list(TypeOfResidence = c("Collective dormitory", "Renting with others", "Renting as a family", "Renting alone", "Owning a living place"), GenderX = c("Male","Female"))

TypeOfResidence

chisq.test(TypeOfResidence,correct=F)

```

##### Section 2 - Chi-square Test for Physical and Mental Status and Lifestyle Behaviours of Rural-to-Urban Migrants by Gender

```{r,  message=FALSE, echo=FALSE}
BMI <- table(healthDataTbl$BMIX, healthDataTbl$GenderX)
dimnames(BMI) <- list(BMIX = c("Under Weight", "Normal", "Overweight/Obesity"), GenderX = c("Male","Female"))

BMI

chisq.test(BMI,correct=F)

```

```{r,  message=FALSE, echo=FALSE}
MentalHealth <- table(healthDataTbl$MentalHealthX, healthDataTbl$GenderX)
dimnames(MentalHealth) <- list(MentalHealthX = c("Normal", "Abnormal"), GenderX = c("Male","Female"))

MentalHealth

chisq.test(MentalHealth,correct=F)

```

```{r,  message=FALSE, echo=FALSE}
Smoking <- table(healthDataTbl$CurrentSmokerX, healthDataTbl$GenderX)
dimnames(Smoking) <- list(CurrentSmokerX = c("Previous smoker/Never smoked", "Current smoker"), GenderX = c("Male","Female"))

Smoking

chisq.test(Smoking,correct=F)

```

```{r,  message=FALSE, echo=FALSE}
Drinking <- table(healthDataTbl$HazardousDrinkX, healthDataTbl$GenderX)
dimnames(Drinking) <- list(HazardousDrinkX = c("Nonhazardous alcohol use", "Hazardous alcohol use"), GenderX = c("Male","Female"))

Drinking

chisq.test(Drinking,correct=F)

```

```{r,  message=FALSE, echo=FALSE}
SleepingTime <- table(healthDataTbl$DailySleepingHoursX, healthDataTbl$GenderX)
dimnames(SleepingTime) <- list(DailySleepingHoursX = c("7-9 Hours/night", "<7 or >9 Hours/night"), GenderX = c("Male","Female"))

SleepingTime

chisq.test(SleepingTime,correct=F)

```

```{r,  message=FALSE, echo=FALSE}
SleepingQuality <- table(healthDataTbl$SleepingQualityX, healthDataTbl$GenderX)
dimnames(SleepingQuality) <- list(SleepingQualityX = c("Nonhazardous alcohol use", "Hazardous alcohol use"), GenderX = c("Male","Female"))

SleepingQuality

chisq.test(SleepingQuality,correct=F)

```

```{r,  message=FALSE, echo=FALSE}
DailyBreakfast <- table(healthDataTbl$DailyBreakfastX, healthDataTbl$GenderX)
dimnames(DailyBreakfast) <- list(DailyBreakfastX = c("Almost Daily Breakfast", "Not Almost Daily Breakfast"), GenderX = c("Male","Female"))

DailyBreakfast

chisq.test(DailyBreakfast,correct=F)

```

```{r,  message=FALSE, echo=FALSE}
DailyFruitsVegetables <- table(healthDataTbl$DailyFruitsVegetablesX, healthDataTbl$GenderX)
dimnames(DailyFruitsVegetables) <- list(DailyFruitsVegetablesX = c("Almost Daily Fruits Vegetables", "Not Almost Daily Fruits Vegetables"), GenderX = c("Male","Female"))

DailyFruitsVegetables

chisq.test(DailyFruitsVegetables,correct=F)

```

```{r,  message=FALSE, echo=FALSE}
DailyRegularMeals <- table(healthDataTbl$DailyRegularMealsX, healthDataTbl$GenderX)
dimnames(DailyRegularMeals) <- list(DailyRegularMealsX = c("Almost Daily Regular Meals", "Not Almost Daily Regular Meals "), GenderX = c("Male","Female"))

DailyRegularMeals

chisq.test(DailyRegularMeals,correct=F)

```

```{r,  message=FALSE, echo=FALSE}
LifestyleScoreX <- table(healthDataTbl$ScoreX, healthDataTbl$GenderX)
dimnames(LifestyleScoreX) <- list(ScoreX = c("Healthy", "Relatively Healthy", "Unhealthy"), GenderX = c("Male","Female"))

LifestyleScoreX

chisq.test(LifestyleScoreX,correct=F)


healthDataTbl$ScoreX <- factor(healthDataTbl$ScoreX,levels=c(1,2,3),
  	labels=c("Healthy", "Relatively Healthy", "Unhealthy")) 
healthDataTbl$GenderX <- factor(healthDataTbl$GenderX,levels=c(1,2),
  	labels=c("Male","Female")) 
densityplot(~healthDataTbl$Score|healthDataTbl$GenderX, main="Lifestyle Score - Gender", xlab="Lifestyle Score")
qplot(GenderX, data=healthDataTbl, geom="bar", fill=ScoreX, xlab="", ylab="Lifestyle Score", main="Lifestyle Score - Gender")

```

##### Section 3 - Association between lifestyle Score and socio-demographic characteristics and phiscal and mental status (By Gender)

* 3.1.1 For Male rural-to-urban migrants (All 13 independent variables available are used in the logistic regression model)

```{r,  message=FALSE, echo=FALSE}

Male <- dplyr::filter(healthData, GenderX == 1)

AGE1 <- cut(Male$AgeX, c(0.5, 1.5,2.5), labels = c("<=32",">32"))
OCCUPATION1 <- cut(Male$Occupation, c(0.5, 1.5,2.5,3.5,4.5,5.5, 6.5), labels = c("Manufacturing", "Construction", "Hospitality", "DomesticSservices", "SmallBusiness", "Recreation/Leisures"))
WORKPLACESCALE1 <- cut(Male$WorkplaceScale, c(0.5, 1.5,2.5,3.5), labels = c("Large","Moderate","Small"))
EDUCATIONATTAINMENT1 <- cut(Male$EducationAttainmentX, c(0.5, 1.5,2.5,3.5,4.5), labels = c("Elementary/Lower","JuniorHigh","HighSchool","College"))
MARITALSTATUS1 <- cut(Male$MaritalStatus, c(0.5, 1.5,2.5,3.5,4.5), labels = c("Married", "Single","Cohabitating","Divorced/Widowed"))
ACCOMPANYCHILD1 <- cut(Male$AccompanyChildX, c(0.5, 1.5,2.5,3.5), labels = c("NoChildren","Cohabitate","ResideElsewhere"))
SALARY1 <- cut(Male$SalaryX, c(0.5, 1.5,2.5,3.5,4.5), labels = c("<1500RMB","1500-2500RMB","2500-3500RMB",">=3500RMB"))
NUMBEROFCITIESRESIDEDIN1 <- cut(Male$NumberOfCitiesResidedInX, c(0.5, 1.5,2.5), labels = c("1-2", ">=3"))
DAILYWORKINGHOURS1 <- cut(Male$DailyWorkingHoursX, c(0.5, 1.5,2.5,3.5,4.5), labels = c("=8","<8","8-11",">=11"))
WEEKLYWORKINGDAYS1 <- cut(Male$WeeklyWorkingDaysX, c(0.5, 1.5,2.5,3.5,4.5), labels = c("<=4","5","6","7"))
RESIDENCE1 <- cut(Male$TypeOfResidence, c(0.5, 1.5,2.5,3.5,4.5,5.5), labels = c("CollectiveDormitory", "Rent(with others)", "Rent(family)", "Rent(alone)", "OwnLivingPlace"))
BMI1 <- cut(Male$BMIX, c(0.5, 1.5,2.5,3.5), labels = c("Underweight", "NormalWeight", "Overweight"))
MENTALHEALTH1 <- cut(Male$MentalHealthX, c(0.5, 1.5,2.5), labels = c("Normal", "Abnormal"))

test1 <- glm(ScoreX~ AGE1 + OCCUPATION1 + WORKPLACESCALE1 + EDUCATIONATTAINMENT1 + MARITALSTATUS1  + ACCOMPANYCHILD1 + SALARY1 + NUMBEROFCITIESRESIDEDIN1 + DAILYWORKINGHOURS1 + WEEKLYWORKINGDAYS1 + RESIDENCE1 + BMI1 + MENTALHEALTH1, data = Male)
summary(test1)

```

* 3.1.2 For Male rural-to-urban migrants (Only 4 significant independent variables (5% significance level) are used in the logistic regression model)

```{r,  message=FALSE, echo=FALSE}
test1X <- glm(ScoreX~  OCCUPATION1 + WORKPLACESCALE1 + DAILYWORKINGHOURS1 + MENTALHEALTH1, data = Male)
summary(test1X)

ci1X <- confint(test1X)

exp(cbind(COR = coef(test1X), ci1X))
```

###### Male - significant risk factor COR visualization

```{r,  message=FALSE, echo=FALSE}
COR = c(1.0, 1.0631474, 1.2081163, 0.9448161, 1.0631395, 1.4486360)
Occupation = c("1Manufacturing", "2Construction", "3Hospitality", "4DomesticServices", "5SmallBusiness", "6Recreation/Leisures")
COROccupation = data.frame(COR,Occupation)
ggplot(COROccupation, aes(x = Occupation, y = COR, fill = Occupation)) + geom_bar(stat = "identity", width = 0.8)
```


```{r,  message=FALSE, echo=FALSE}
COR = c(1.0, 0.9873853, 1.1189892)
WorkplaceScale = c("1Large","2Moderate","3Small")
CORWorkplaceScale = data.frame(COR,WorkplaceScale)
ggplot(CORWorkplaceScale, aes(x = WorkplaceScale, y = COR, fill = WorkplaceScale)) + geom_bar(stat = "identity")
```


```{r,  message=FALSE, echo=FALSE}
COR = c(0.9728401, 1.0, 1.0224851, 1.1472823)
DailyWorkingHours = c("1.<8hr","2.=8hr","3.8-11hr","4.>=11hr")
CORDailyWorkingHours = data.frame(COR,DailyWorkingHours)
ggplot(CORDailyWorkingHours, aes(x = DailyWorkingHours, y = COR, fill = DailyWorkingHours)) + geom_bar(stat = "identity")
```


```{r,  message=FALSE, echo=FALSE}
COR = c(1.0, 1.4592257)
MentalHealth = c("1Normal", "2Abnormal")
CORMentalHealth = data.frame(COR,MentalHealth)
ggplot(CORMentalHealth, aes(x = MentalHealth, y = COR, fill = MentalHealth)) + geom_bar(stat = "identity")
```


* 3.2.1 For Female rural-to-urban migrants (All 13 independent variables available are used in the logistic regression model)

```{r,  message=FALSE, echo=FALSE}

Female <- dplyr::filter(healthData, GenderX == 2)

AGE2 <- cut(Female$AgeX, c(0.5, 1.5,2.5), labels = c("<=32",">32"))
OCCUPATION2 <- cut(Female$Occupation, c(0.5, 1.5,2.5,3.5,4.5,5.5, 6.5), labels = c("Manufacturing", "Construction", "Hospitality", "DomesticSservices", "SmallBusiness", "Recreation/Leisures"))
WORKPLACESCALE2 <- cut(Female$WorkplaceScale, c(0.5, 1.5,2.5,3.5), labels = c("Large","Moderate","Small"))
EDUCATIONATTAINMENT2 <- cut(Female$EducationAttainmentX, c(0.5, 1.5,2.5,3.5,4.5), labels = c("Elementary/Lower","JuniorHigh","HighSchool","College"))
MARITALSTATUS2 <- cut(Female$MaritalStatus, c(0.5, 1.5,2.5,3.5,4.5), labels = c("Married", "Single","Cohabitating","Divorced/Widowed"))
ACCOMPANYCHILD2 <- cut(Female$AccompanyChildX, c(0.5, 1.5,2.5,3.5), labels = c("NoChildren","Cohabitate","ResideElsewhere"))
SALARY2 <- cut(Female$SalaryX, c(0.5, 1.5,2.5,3.5,4.5), labels = c("<1500RMB","1500-2500RMB","2500-3500RMB",">=3500RMB"))
NUMBEROFCITIESRESIDEDIN2 <- cut(Female$NumberOfCitiesResidedInX, c(0.5, 1.5,2.5), labels = c("1-2", ">=3"))
DAILYWORKINGHOURS2 <- cut(Female$DailyWorkingHoursX, c(0.5, 1.5,2.5,3.5,4.5), labels = c("=8","<8","8-11",">=11"))
WEEKLYWORKINGDAYS2 <- cut(Female$WeeklyWorkingDaysX, c(0.5, 1.5,2.5,3.5,4.5), labels = c("<=4","5","6","7"))
RESIDENCE2 <- cut(Female$TypeOfResidence, c(0.5, 1.5,2.5,3.5,4.5,5.5), labels = c("CollectiveDormitory", "Rent(with others)", "Rent(family)", "Rent(alone)", "OwnLivingPlace"))
BMI2 <- cut(Female$BMIX, c(0.5, 1.5,2.5,3.5), labels = c("Underweight", "NormalWeight", "Overweight"))
MENTALHEALTH2 <- cut(Female$MentalHealthX, c(0.5, 1.5,2.5), labels = c("Normal", "Abnormal"))

test2 <- glm(ScoreX~ AGE2 + OCCUPATION2 + WORKPLACESCALE2 + EDUCATIONATTAINMENT2 + MARITALSTATUS2  + ACCOMPANYCHILD2 + SALARY2 + NUMBEROFCITIESRESIDEDIN2 + DAILYWORKINGHOURS2 + WEEKLYWORKINGDAYS2 + RESIDENCE2 + BMI2 + MENTALHEALTH2, data = Female)
summary(test2)

```

* 3.2.2 For Female rural-to-urban migrants (Only 6 significant independent variables (5% significance level) are used in the logistic regression model)

```{r,  message=FALSE, echo=FALSE}
test2X <- glm(ScoreX~  OCCUPATION2 + MARITALSTATUS2 + SALARY2 + NUMBEROFCITIESRESIDEDIN2 + DAILYWORKINGHOURS2 + MENTALHEALTH2, data = Female)
summary(test2X)

ci2X <- confint(test2X)

exp(cbind(COR = coef(test2X), ci2X))
```

###### Female - significant risk factor COR visualization


```{r,  message=FALSE, echo=FALSE}
COR = c(1.0, 0.9911594 , 1.1868136 , 1.1542077 , 1.1395947 , 1.7668876 )
Occupation = c("1Manufacturing", "2Construction", "3Hospitality", "4DomesticServices", "5SmallBusiness", "6Recreation/Leisures")
COROccupation = data.frame(COR,Occupation)
ggplot(COROccupation, aes(x = Occupation, y = COR, fill = Occupation)) + geom_bar(stat = "identity", width = 0.8)
```


```{r,  message=FALSE, echo=FALSE}
COR = c(1.0, 1.2531444 , 1.1591268 , 1.1350338 )
MaritalStatus = c("1Married", "2Single","3Cohabitating","4Divorced/Widowed")
CORMaritalStatus = data.frame(COR,MaritalStatus)
ggplot(CORMaritalStatus, aes(x = MaritalStatus, y = COR, fill = MaritalStatus)) + geom_bar(stat = "identity")
```


```{r,  message=FALSE, echo=FALSE}
COR = c(1.0, 0.9290095 , 0.9372682 , 1.1620696 )
Salary = c("1.<1500RMB","2.1500-2500RMB","3.2500-3500RMB","4.>=3500RMB")
CORSalary = data.frame(COR,Salary)
ggplot(CORSalary, aes(x = Salary, y = COR, fill = Salary)) + geom_bar(stat = "identity")
```


```{r,  message=FALSE, echo=FALSE}
COR = c(1.0, 1.0856702 )
NumberOfCitiesResidedIn = c("1. 1-2 cities", "2. >=3 cities")
CORNumberOfCitiesResidedIn = data.frame(COR,NumberOfCitiesResidedIn)
ggplot(CORNumberOfCitiesResidedIn, aes(x = NumberOfCitiesResidedIn, y = COR, fill = NumberOfCitiesResidedIn)) + geom_bar(stat = "identity")
```


```{r,  message=FALSE, echo=FALSE}
COR = c(1.0775489 , 1.0, 1.1026676 , 1.0688807 )
DailyWorkingHours = c("1.<8hr","2.=8hr","3.8-11hr","4.>=11hr")
CORDailyWorkingHours = data.frame(COR,DailyWorkingHours)
ggplot(CORDailyWorkingHours, aes(x = DailyWorkingHours, y = COR, fill = DailyWorkingHours)) + geom_bar(stat = "identity")
```


```{r,  message=FALSE, echo=FALSE}
COR = c(1.0, 1.3798815 )
MentalHealth = c("1Normal", "2Abnormal")
CORMentalHealth = data.frame(COR,MentalHealth)
ggplot(CORMentalHealth, aes(x = MentalHealth, y = COR, fill = MentalHealth)) + geom_bar(stat = "identity")
```

